Wikipedia Text Mining and Entropy Analysis

### 2019-03-04 wiki_entropy/wiki_clustering.Rmd
clustering issues

wf <- wals.feature(FEATURES) 
fair_wf <- wf[rowSums(!is.na(wf)) > 50,] %>%
  filter(language %in% LANGUAGES) %>%
  select(-wals.code, -latitude, -longitude, -glottocode) %>%
  as_data_frame()

@@

wa <- fair_wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(`1A`:`19A`, language) %>%
  group_by(language) %>%
  slice(1) %>%
  gather(feature, value, `1A`:`19A`) %>%
  group_by(feature) %>%
  mutate(value = factor(value)) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  column_to_rownames("language") %>%
  sapply(as.factor) %>%
  as_data_frame() %>%
  MIMCA(ncp = 1, maxiter = 100000, threshold = 1e-1)

wa <- as.data.frame(wa[[1]][[99]]) 
wa$language <- unique(phon_wf$language)
```

>>>>

fair_wf <- wf[rowSums(!is.na(wf)) > 50,] %>%
  filter(language %in% LANGUAGES) %>%
  select(-wals.code, -latitude, -longitude, -glottocode) %>%
  as_tibble() %>%
  clean_names()

@@

wa <- fair_wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(x1a:x19a, language) %>%
  group_by(language) %>%
  slice(1)

wa_langs <- wa %>%
  gather(measure, value, -language) %>%
  group_by(language) %>%
  summarise(value = mean(!is.na(value))) %>%
  arrange(desc(value)) %>%
  filter(value > .6) %>% 
  pull(language)

wa_sub <- wa %>%
  filter(language %in% wa_langs) %>%
  column_to_rownames("language")
 # mutate_each(~as.numeric(as.factor(.x)))

wa_out <- wa_sub %>%
  select(-x14a:-x17a, -x9a,-x10a) %>%
  slice(1:5) %>%
  MIMCA(ncp = 1)

wa_imputed <- wa_out[["res.MI"]] %>%
  map(~mutate(.x, language = wa_langs)) %>%
  bind_rows(.id = "boot") %>%
  group_by(language, boot) %>%
  gather(measure, value, -language, -boot) %>%
  group_by(language, measure) %>%
  summarise(value = mean(value, na.rm = T)) %>%
  spread(measure, value)
```
